### 2021-03-18 paper.Rmd
all figures done

> figure 4 diagram illustrating different types of target generation

>>>>

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{figures/notation-target-gen.pdf}
\caption{A comparison of guided and grand tour path in the PCA reduced space. The start point of tour paths is smaller and ligher than the end point. Guided tour optimises the index value iteratively and finishes the search quickly while grand tour wanders in the parameter space to look at possible interesting projections.}
\label{fig:notation-target-gen}
\end{figure}
